% !TEX program = xelatex
\documentclass{resume}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Adarsh Chaudhary}

\basicInfo{
  \email{adarshgc.cs.20@nitj.ac.in} \textperiodcentered\ 
  \phone{(+91) 9805232954} \textperiodcentered\ 
  \linkedin[Adarsh Chaudhary]{https://www.linkedin.com/in/adarsh-gopal-chaudhary-2a382220b/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Dr. B. R. Ambedkar National Institute of Technology }, Jalandhar}{2020 -- Present}
\textit{Bachelor of Technology}  Computer Science Engineering (CGPA 7.63), expected June 2024
\datedsubsection{\textbf{Gian Jyoti Global School}, Mohali, Punjab}{2019}
\textit{12TH Standard} (76.8 percent)
\datedsubsection{\textbf{Mount Carmel Sr. Sec. School}, Una, H.P.}{2017}
\textit{10TH Standard} (88.6 percent)

\section{\faUsers\ Projects}
\datedsubsection{\textbf{Summarize} }{\website{https://elegant-sfogliatella-7b23a0.netlify.app/}}
\role{GitLab: \gitlab{clopx/Summary.git}}{}
A highly efficient article summarization tool that generates concise summaries from lengthy articles, ensuring quick and accurate information retrieval.
\begin{itemize}
  \item Developed an article summarization tool using Vite, React, and GPT-3.0.
  \item Implemented Tailwind CSS for sleek and responsive styling.
  \item Deployed the project on Netlify for easy accessibility and scalability.
\end{itemize}

\datedsubsection{\textbf{MagicDex}}{\website{https://magicdex-henna.vercel.app/}}
\role{NextJs, Tailwind, Typescript}{GitLab: \gitlab{clopx/magicDex.git}}
A web application that functions as a comprehensive Pokedex for Magic: The Gathering cards, enabling users to effortlessly browse, explore, and access a vast collection of cards from the game.x
\begin{itemize}
  \item Developed a dynamic web application utilizing Next.js, Tailwind CSS, and TypeScript, serving as an extensive Pokedex for Magic: The Gathering cards.
  \item Integrated with the Scryfall API to provide users with the ability to view original artwork for all cards, offering an immersive visual experience.
  \item  Implemented search functionality across all available sets, allowing users to easily find specific cards based on various criteria, enhancing accessibility and convenience.
\end{itemize}

\datedsubsection{\textbf{Document Denoising}}{\href{https://colab.research.google.com/drive/1o8Mb3ygvO14njDlJq1FGyCmmWQjviPNB?usp=sharing}{Google Colab} }
Utilizing autoencoder for document denoising, enhancing document quality and removing noise.
\begin{itemize}
  \item Leveraged PyTorch to implement autoencoders for document denoising.
  \item Autoencoders effectively learned and extracted meaningful features, enhancing document clarity.
  \item Improved document quality by reducing noise, errors, and irrelevant information.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python, JavaScript/TypeScript, C/C++
  \item Platform: Linux
  \item Framework: Next Js, TensorFlow, Tailwind
  \item Development: Full stack, Machine Learning
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Gitlab: https://gitlab.com/neoupie
  \item GitHub: https://github.com/neocpx
  \item Languages: English - Fluent, Punjabi - Fluent, Hindi - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
